\subsubsection{Week 1}
No progress this week.

Plan for next week is to implement more of the telemetry interface.

No problems.

\subsection{Week 2}
No progress this week.

Finish implementing telemetry.

No blockers.

\subsubsection{Week 3}
This week, in light of the SD card still being unfinished, I implemented logging to the eeprom on the microcontroller. The eeprom only has 4 kilobytes of available memory, so it is only a mediocre replacement. We no longer have time to fix the SD card library we are using, so we must pursue other means of telemetry. Telemetry via the provided telemetry pins is fully implemented. Telemetry via SD card is partially implemented, but cannot be finished if the SD card library can't be fixed. Telemetry via eeprom is fully implemented. Until SD card is unblocked, the telemetry component is complete.

Last week, we had a team meeting. We have further split up the work, and my part is to meet with the instructors to review deadlines. I also plan on getting the poster completed and submitted. I will also be taking control of writing a readme for the github repo and copy test code into science mode file.

No problems.

\subsubsection{Week 4}
This week I am making sure me and my team is ready for expo. I am following up with important people and assignments to make sure everything is complete and deadlines are being met. This includes but is not limited to making finals edits on our poster, getting out client's signature for the poster, submitting the poster, and making sure everyone has signed the necessary forms for expo.

I have completed both the video and telemetry components. I have only the data processing component left to implement as my portion of the project, but that is currently blocked until we receive further instruction from NASA. I have nothing left to implement for this project. I will spend the next week getting ready for expo and working on my presentation.

I am waiting for after Integration testing with Wallops and we receive the format of telemetry data. Then the implementation of the data processing component can begin. I will not be directly working on this component, but rather guiding James on implementing the component.

\subsubsection{Week 5}
This week I made some minor changes to the telemetry code.

Next week I plan to support Amber and Helena with development of the rest of the system.

No blockers.

\subsubsection{Week 6}
This week I made some more minor tweaks to the telemetry code. I also sat down with Amber for 2 hours and worked on making the code in the repo to compiler. We also added a bunch of missing code in the off and retract phases. We also refactored a bunch of code to make it more readable.

Next week will be spent waiting for Helena to finish writing the code for the science phase.

Blocking on science phase being finished.
