\newglossaryentry{payload}{
name=payload,
description={A subsection of a rocket that is not essential to the rocket's operation. A payload is placed in a can, mounted on a standard base plate. A payload completes some specific task.}
}

\newglossaryentry{can}{
name=can,
description={A can is a segment of the rocket in which payloads can be placed. A can constitutes a standard length of rocket, defined by the RockSat-X program.}
}

\newglossaryentry{Arm Assembly}{
name={Arm Assembly},
description={The Hephaestus Arm Assembly includes the arm, the rotating arm base, the camera, and base. It is the portion of the payload that is extended during Science mode.}
}

\newglossaryentry{api}{
name=API,
description={Application Programming Interface. The set of functions and classes that a given library exposes for other programs to make use of its provided functionality.}
}

\newglossaryentry{port}{
name=port,
description={To transfer software from one system or machine to another.}
}

\newglossaryentry{ter}{
name=TE-R,
description={The TE-R line is a redundant electrical input to the system that enables at a predetermined time during flight.}
}

\newglossaryentry{te1}{
name=TE-1,
description={The TE-1 line is an electrical input to the system that enables at a predetermined time during flight.}
}

\newglossaryentry{replay}{
name=replay,
description={To replay a dataset is to reproduce preexisting data in a manner that
simulates how it was generated, e.g. output the data in the same timeline that each
data point was generated.}
}

\newglossaryentry{plot}{
name=plot,
description={An interactive window generated by the Python library matplotlib to
display some dataset on an x and y axis.}
}

\newglossaryentry{apogee}{
name=apogee,
description={The point at which the rocket has finished its ascent and payloads
are allowed to deploy.}
}

\newglossaryentry{matplotlib}{
name=matplotlib,
description={A Python library for drawing and manipulating graphs.}
}

\newglossaryentry{binstring}{
name=binary string,
description={An ordered sequence of 1's and 0's.}
}

\newglossaryentry{deployable}{
name=deployable,
description={Any portion of the payload that is expanded from its original 
configuration once in a space-like environment.}
}

\newacronym{psu}{PSU}{Portland State University}
\newacronym{psas}{PSAS}{Portland State Aerospace Society}
\newacronym{gui}{GUI}{Graphical User Interface}
\newacronym{wff}{WFF}{Wallops Flight Facility}
\newacronym{osu}{OSU}{Oregon State University}
\newacronym{OBC}{OBC}{On-Board Computer}
