\documentclass[letterpaper,10pt]{article}

\usepackage{geometry}
\usepackage{hyperref}
\usepackage{tabulary}
\usepackage[nopostdot]{glossaries}
\usepackage[pdftex]{graphicx}
\usepackage{tikz}
\usepackage{wrapfig}
\geometry{textheight=8.5in, textwidth=6in}
\newenvironment{bottompar}{\par\vspace*{\fill}}{\clearpage}

\makeglossaries
\loadglsentries[main]{Glossary}

\title{Progress Report For RockSat-X Payload - Hephaestus}
\author{Helena~Bales, Amber~Horvath, and Michael~Humphrey\\ \\ CS461 - Fall 2016}

\parindent = 0.0 in
\parskip = 0.1 in

\begin{document}
\maketitle

\begin{abstract}
\end{abstract}

\begin{bottompar}
Approved By
\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_
Date \_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_ \\


Approved By
\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_
Date \_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_ \\


Approved By
\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_
Date \_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_ \\


Approved By
\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_
Date \_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_ \\
\end{bottompar}

\clearpage
\tableofcontents
\clearpage

\section{Introduction}
The Hephaestus Payload is a rocketry payload that will fly onboard the 2016-2017 RockSat-X rocket. 
The rocket will be launched from Wallops Flight Facility filled with student-made payloads. 
The Hephaestus payload will be made up of a deployable arm and a video camera. The arm will perform 
a series of motions that will be recorded by the video camera and sensors. Following the experiment, the 
arm will retract back into the rocket. The Hephaestus mission will be Oregon State University's first 
space mission and will prove not only our ability to develop a space-ready payload, but also the 
viability of construction in space using a robotic arm.

\subsection{Document Overview}
This document will serve as a progress update following Fall term of 2016. At the time of writing, we 
have worked on the Hephaestus payload for ten weeks. This document will include an overview of the 
project goals and purpose, our work so far, the problems we have encountered, and a retrospective.

\section{Project Overview}
\subsection{Project Purpose}
The Oregon State University RockSat-X team will demonstrate that an autonomous robotic arm can locate predetermined
 targets around the payload under microgravity conditions by using precise movements. 
The technical actions performed by this demonstration will illustrate a proof of concept for creating assemblies, 
autonomous repairs, and performing experiments in space.
\subsection{Mission Success Criteria}
The Oregon State University RockSat-X team will demonstrate that an autonomous robotic arm can locate predetermined targets around the 
payload under microgravity conditions by using precise movements. The technical actions performed by this demonstration will illustrate 
a proof of concept for creating assemblies, autonomous repairs, and performing experiments in space. 
The mission objectives are to deploy a robotic payload capable of moving with four axes of freedom; deploy a Camera with a single axis 
of freedom;
enact a series of pre-scripted movements by the arm including contact with stationary sensors;
coordinate the Camera to track arm movements and record demonstration; and
store sensor data for when arm is at rest, and when it comes into contact with station sensors.
\section{Current Progress}
\subsection{Helena Balse}
\input{Helena}
\subsection{Amber Horvath}
\input{AmberProgressUpdate}
\subsection{Michael Humphrey}
\input{michael-progress-update}
\section{Retrospective}
\input{retrospective}

\section{Conclusion}

\end{document}
